---
title: "Cucurbit crops: gourds"
author: 
  - Deependra Dhakal 
date: 2019
output:   
  beamer_presentation:
    incremental: false  
    theme: "Frankfurt"  
    colortheme: "beaver"
    toc: true   
    slide_level: 2
    keep_tex: true
    includes:
      in_header: beamer_header.tex
classoption: "aspectratio=169"
header-includes: 
- \AtBeginSubsection{}
bibliography: ['../bib/references.bib']
---

```{r setup, include=FALSE}
library(knitr)
require(tidyverse)
set.seed(453)
# invalidate cache when the package version changes
knitr::opts_chunk$set(tidy = FALSE, echo = FALSE, 
                  message = FALSE, warning = FALSE,
                  out.width = "45%")
options(knitr.table.format = "latex")
options(knitr.kable.NA = "", digits = 2)
options(kableExtra.latex.load_packages = FALSE)
```

# Introduction

## Background

- Consist several genera indigenous to Africa, India, Asia, and the Americas.
- Generally eaten when immature, some edible as they ripe.
- Cylindrical, discoid, or bottle-shaped.
- Seeds found in the central cavity.
- Mostly grown in Asia and parts of Africa.

##

```{r gourds-intro, include=TRUE, results='asis', echo=FALSE}
gourd_crops <- readxl::read_xlsx("../data/cucurbitaceae.xlsx", sheet = "gourds")

gourd_crops %>% 
  mutate(`Scientific Name` = str_replace(string = `Scientific Name`, 
                                         pattern = "(^[:alpha:]*\\s[:alpha:]*)", 
                                         replacement = "\\\\textit{\\1}")) %>% 
  knitr::kable(format = "latex", caption = "Nomenclature of gourds", booktabs = TRUE, escape = FALSE) %>%
  kableExtra::kable_styling(bootstrap_options = "striped")
```

## Uses

- Sponge gourd upon maturing is fibrous and 
can be used as rough sponge or scrub pad.
- Airtight container (Calabash gourd)
- Can be stored after slice drying for later use as vegetable.
- Some are even eaten raw.

# Bottle gourd

## Introduction

- Common in Nepal and India, but grown in Ethiopia, Africa, Central America and warmer regions.
- Fruits' shape resemble to that of a bottle.
- Mostly yellowish-green or cream colored, relatively soft in texture, with white pulp and large white seeds.
- Used for making sweets and pickles.
- Beneficial for jaundice patients, in those with digestive problems, cough, nightblindness, etc.
- Monoecious annual vine with large oxalate oval leaves and branched tendrils spreading or climbing 3-15m.
- Foliage pubescent and emits musky odor when bruised.
- Flowers large white, borne on slender peduncles, open in the evening and may remain open until the middle of the following day.
- Fruits vary in shape and sizes(10-90cm in length)

## Cultivation: Climate

- Tropical crop(hot and humid climate)
- Optimum temperature: $24-27^\circ C$
- Highly sensitive to photoperiod
- Short day and humid climate promote femaleness

## Cultivation: Soil

- Best on sandy loam with high OM content
- Well drained
- pH: 6-7
- River bed farming is also successful

## Cultivation: Propagation

- Seeds(450-500/100g)
- Seed retains viability for long periods(upto 34 years)

## Cultivation: Cultural Practices

- Shallow rooted crop
- Fine bed preparation
- Direct sowing on raised beds, in furrows, or trenches or pits
- Two seeds per hill on either sides of raised beds or furrows
- Spacing: 2.5\*2m or 2-3\*1.5m
- Pit: 90\*90\*60cm deep, filled with FYM and topsoil
- 3-4 seeds per pit
- 45 t/ha FYM
- 40-60:40-60:60-80 kg/ha NPK
- Nitrogen in split doses(Basal and at vining stage)
- Pruning to exert favorable effects on fruit yield

## Cultivation: Interculture

- Shallow interculture operations needed
- Hand weeding(2-3 times)
- Pre-emergence herbicide: linuron @ 0.5kg/ha or alachlor 2.5 kg/ha

## Cultivation: Irrigation

- Immediately after seed sowing to promote germination
- High humidity promotes prolific bearing
- Irrigation every 3-4 days in warm weather

## Cultivation: Maturity and Harvesting

- Fruit setting increased by maleic hydrazide spray(400 ppm), boron(3 ppm) and calcium (20 ppm)
- Ready for harvest approx. 60 DAS
- 12-15 days after fruit set to reach marketable size
- Picking every 4-5 days

# Bitter gourd

## Cultivation: Climate and Soil

- Grown in tropical or subtropical climates, but warm and hot climate best for growth
- Most resistant to low temperatures than other cucurbits
- Optimum temp: $24^\circ C-27^\circ C$
- Short day promotes female flower production
- Grow on sandy to loamy soils
- Optimum pH: 6-6.7

## Cultivation: Propagation

- Seed propagated commercially
- Have hard seed coat, impermeable to water
- Heavy seeds, and retain viability for upto 45 years
- Cultural Practices
- Seeds sown in raised beds or pits
- Raised beds: 1.2-1.5m wide beds, 60 cm wide furrows between beds
- Spacing: 1.5-2m between rows, 60-120cm between plants

##

- Pit planting: 60\*60\*45 cm deep, plants spaced at 1.8-2.4cm apart with two seeds per hill
- Seed rate: 4.5-6kg/ha
- Training or staking required, mostly when grown as rainy season crop
- Bowers erected 6 ft. from ground level using wooden poles. Strong poles 10 ft. in length and 4 cm in diameter fixed 45 cm deep in soil, 5 m apart. All poles connected by wire. 16-gauge wires stretched over the 10-gauge wires 60 cm apart, crosswise.
- Kniffens may also be prepared by wooden poles and wire

## Cultivation: Fertilization and manuring

- 60-80 kg N, 70-90 kg P, 60-70 kg K per hectare
- Nitrogen best applied in split doses(latter half \@initial fruit-set stage)

## Cultivation: Irrigation

- First, Immediately after sowing
- At regular intervals of 5-7 days

## Cultivation: Weed management

- Interculture to ensure proper spread of crop
- Weedicides: alachlor and butachlor \@2.5 kg ai/ha

## Cultivation: Maturity and harvest

- Crop takes about 55-110 days from seed sowing to first harves
- Fruits picked while still tender
- Picking done every 2-3 days
- Yellowing of fruit indicated ripening, which is unfit for consumption
- Fruits storable for 35 days under cool and shady conditions

# Pointed gourds

## Cultivation: Propagation

- Crop is dioecious
- Vegetatively propagated with vine cuttings and root suckers
- Seed propagation has poor germination
- 50% plants may be non-fruiting(male) types
- 10-12% male plants is adequate
- Generally, early maturing varieties with fewer nodes bear pistillate flowers
- Cuttings transplanted in August in upland and November in riverbeds
- Spacing: 2 * 2 m
- Root cuttings transpalnted in second half of October
- Vine cuttings of length 1-1.5m cut and folded in a figure of "8" or ring, and planted in pits with mixture of FYM and soil and buried 10 cm deep.

# Snake gourds

# Sponge gourds

# Ash gourds

# Cultivation outline

```{r cultivation-outline, include=TRUE, results='asis', echo=FALSE}
cucurbits_cultivation <- readxl::read_xlsx("../data/cucurbitaceae.xlsx", sheet = "planting")

cucurbits_cultivation %>% 
  knitr::kable(format = "latex", 
               caption = "Cultivation outline of gourds", booktabs = TRUE) %>% 
  kableExtra::kable_styling(latex_options = "striped", 
                            font_size = 6) %>% 
  kableExtra::column_spec(1:9, width = c("5em", "6em", "8em", "8em", "8em", "5em", "5em", "5em", "5em"))
```

# Bibliography

## References

```{r bib, include=FALSE}
# create a bib file for the R packages used in this document
# knitr::write_bib(c('base', 'rmarkdown', "knitr", "tidyverse"), file = '../bib/references.bib')
```
